Location of Marine fish - general Farms

### 2021-03-23 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
checked over sources again
Finished reorganizing data

#  [1] "Albania"                  "Australia"                "Bangladesh"               "Cambodia"                
#  [5] "China"                    "China, Hong Kong SAR"     "Costa Rica"               "Croatia"                 
#  [9] "Cyprus"                   "Egypt"                    "France"                   "Greece"                  
# [13] "India"                    "Indonesia"                "Iran (Islamic Rep. of)"   "Israel"                  
# [17] "Italy"                    "Japan"                    "Korea, Republic of"       "Malaysia"                
# [21] "Malta"                    "Mauritius"                "Mexico"                   "Norway"                  
# [25] "Panama"                   "Philippines"              "Portugal"                 "Saudi Arabia"            
# [29] "Singapore"                "Spain"                    "Taiwan Province of China" "Thailand"                
# [33] "Tunisia"                  "Turkey"                   "United Arab Emirates"     "United States of America"
# [37] "Viet Nam"     
```

## explore
https://gis.asc-aqua.org/arcgis_app/
Maps from ASC

@@

Now we will map the remaining countries with marine finfish farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of finfish farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
 - Lastly, if there is no evidence of marine finfish farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia for bivalves).

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "Allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

@@

# read in shp
farms_all <- ASC_finfish %>%
  cbind(iso) %>%
  dplyr::filter(!(crt_cnt %in% c("Denmark", "Germany", "Netherlands")))

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

## save farm location
write.csv(farms_all_fin, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/ASC_finfish_farm_lat_lon.csv"), row.names = FALSE)

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Cyprus" ~ "CYP", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Greece" ~ "GRC",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

 write_csv(farms_eu_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_ESP_CYP_NOR_GRC_MLT.csv"))

@@

## Italy
From http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/italy/en/

Source:
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

@@

farms_ita <- data.frame(do.call(rbind, st_geometry(ita_pts_latlon))) 
names(farms_ita) <- c("lon", "lat")
farms_ita <- farms_ita %>%
  mutate(iso3c="ITA") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_ita, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_ita.csv"))

@@

mapview(farms_ita)
```

@@

Source:
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

@@

farms_fra <- data.frame(do.call(rbind, st_geometry(fra_pts_latlon))) 
names(farms_fra) <- c("lon", "lat")
farms_fra <- farms_fra %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "France", "FRA", "ISR")) %>%
  dplyr::select(-country, -geometry) %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_fra, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_fra_isr.csv"))

farms_fra <-  st_as_sf(farms_fra, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_fra)
```

@@

Source: 
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

@@

mapview(indo_aqua)

@@

farms_idn <- data.frame(do.call(rbind, st_geometry(idn_pts_latlon))) 
names(farms_idn) <- c("lon", "lat")
farms_idn <- farms_idn %>%
  mutate(iso3c = "IDN") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_idn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_idn.csv"))

farms_idn <-  st_as_sf(farms_idn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_idn)
```

## Portugal
 - https://www.ine.pt/xportal/xmain?xpid=INE&xpgid=ine_publicacoes&PUBLICACOESpub_boui=435690295&PUBLICACOESmodo=2&fbclid=IwAR0-_SHYtw2XGUAXdx71RGer284Vk_u40HYKXyJzeFbpdnsHydKgAfomTvU
 - National Institute of Statistics for Portugal 
 - There is a csv table, "q5_1.csv", which has the number of farms listed by type of system. I will assume that tanks are for finfish, since [this website](https://rea.apambiente.pt/content/aquaculture-production?language=en) says that the tanks are for **fish production**, and floating structures are for **bivalve molluscs**. Located here "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Portugal/EPesca_2019.xlsx"
 - According to the table, by these criteria, there are 112 marine tank farm systems in Portugal. 
 - I will equally allocate 112 points along the coast of Portugal.

Source: 
Estatísticas da Pesca, 2020. . Instituto Nacional de Estatística. [Accessed December 21, 2020]

```{r}
world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
plot(world)

portugal <- ne_countries(scale = 10, country = "Portugal", returnclass = "sf")

#info of our spatial vector object
portugal
mapview(portugal)
plot(portugal)

world <- st_as_sf(world)

portugal_world_crs <- st_transform(portugal, crs(world))

portugal_world_crop <- st_crop(world, portugal_world_crs) #%>%
 # dplyr::filter(scalerank == 5) ## filter for the appropriate island
plot(portugal_world_crop)
mapview(portugal_world_crop)

portugal_crop <- as(portugal_world_crop, "Spatial")

portugal_points_lines <- sample.line(portugal_crop, n = 380) ## equally place the number of farms along the coastline 
class(portugal_points_lines)
plot(portugal_points_lines)

portugal_points <- st_as_sf(portugal_points_lines)
mapview(portugal_points)

portugal_points_final <- portugal_points[253:364, ] ## grab the appropriate number of points
mapview(portugal_points_final)

## now prep dataframe for lat lon points
prt_pts <- st_centroid(portugal_points_final)

prt_pts_latlon <- st_transform(prt_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_prt <- data.frame(do.call(rbind, st_geometry(prt_pts_latlon)))
names(farms_prt) <- c("lon", "lat")

farms_prt_final <- farms_prt %>%
  mutate(iso3c = "PRT") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

## visualize it 
farms_prt <-  st_as_sf(farms_prt, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_prt)

## write to farms folder 
write_csv(farms_prt_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_prt.csv"))
```

@@

The only species the FAO reports for Iran is "Marine fishes nei", and I can't find any information on number of marine farms there might be in Iran. Therefore I will place one farm on the Caspian Sea coast.

@@

farms_irn <- data.frame(lat = c(37.392419247868425),
                        lon = c(50.1602963496454)) %>%
  mutate(iso3c = "IRN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

write_csv(farms_irn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_irn.csv"))

## visualize it 
farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_irn)
```

## China 
Can't find any datasets of marine finfish farm locations in China. Therefore I will place one farm on the coast of China.

@@

farms_chn <- data.frame(lat = c(26.649767732301385),
                        lon = c(119.94149300994019)) %>%
  mutate(iso3c = "CHN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

write_csv(farms_chn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_chn.csv"))

## visualize it 
farms_chn <-  st_as_sf(farms_chn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_chn)
```

@@

@@

farms_sau <- data.frame(lat = c(20.27293672234808),
                        lon = c(40.03614937279944)) %>%
  mutate(iso3c = "SAU") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_sau, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_sau.csv"))

@@

Can't find any datasets of marine finfish farm locations. Therefore I will place one farm on the coast. It probably doesn't matter, since Mauritius is so small anyways.

@@

farms_mus <- data.frame(lat = c(-20.005039247819017),
                        lon = c(57.67022708374523)) %>%
  mutate(iso3c = "MUS") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

write_csv(farms_mus, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_mus.csv"))

## visualize it 
farms_mus <-  st_as_sf(farms_mus, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_mus)
```

@@

farms_are <- data.frame(lat = c(25.604715925918068),
                        lon = c(56.340214330776234)) %>%
  mutate(iso3c = "ARE") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

write_csv(farms_are, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_are.csv"))

@@

 - I'll place 20 points along the coast of Monastir

@@

```{r}
## load municipality shapefile, downloaded from here: https://gadm.org/download_country_v3.html
tunisia <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/Tunisia/gadm36_TUN_shp/gadm36_TUN_1.shp")) %>%
  dplyr::filter(NAME_1 == "Monastir")

mapview(tunisia)

## OR if you don't municipality and only country info you could use this: 
# tunisia <- rnaturalearth::ne_countries(country = "Tunisia")

world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
plot(world)
class(world)

#info of our spatial vector object
tunisia
mapview(tunisia)

world <- st_as_sf(world)

tunisia_world_crs <- st_transform(tunisia, crs(world))

tunisia_world_crop <- st_crop(world, tunisia_world_crs) 
plot(tunisia_world_crop)
mapview(tunisia_world_crop)

tunisia_crop <- as(tunisia_world_crop, "Spatial")
class(tunisia_crop)
mapview(tunisia_crop)

tunisia_points_lines <- sample.line(tunisia_crop, n = 20) ## equally place the number of farms along the coastline 
class(tunisia_points_lines)
plot(tunisia_points_lines)

tunisia_points <- st_as_sf(tunisia_points_lines)
mapview(tunisia_points)

## now prep dataframe for lat lon points
tun_pts <- st_centroid(tunisia_points)

tun_pts_latlon <- st_transform(tun_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_tun <- data.frame(do.call(rbind, st_geometry(tun_pts_latlon)))
names(farms_tun) <- c("lon", "lat")

farms_tun_final <- farms_tun %>%
  mutate(iso3c = "TUN") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

## visualize it 
farms_tun <-  st_as_sf(farms_tun, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_tun)

## write to farms folder 
write_csv(farms_tun_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_tun.csv"))
```

@@

Milkfish:
https://digitalarchive.worldfishcenter.org/bitstream/handle/20.500.12348/3610/Pub%20TR4%206.pdf?sequence=1&isAllowed=y
 - I will use the respondents from the survey, and place the appropriate number of points in each location (table located on page 6, I will only use "gatherers"). This is a really old paper, but it is the best I can find. 42 total points

@@

Combine milkfish and grouper points

```{r}
all_points_twn <- rbind(milkfish_points, grouper_points) %>%
  dplyr::mutate(iso3c = "TWN") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

## write to farms folder 
write_csv(all_points_twn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_twn.csv"))

@@

9.423478373794573, -84.20910189917947

@@

```{r}
farms_cri <- data.frame(lat = c(9.423478373794573),
                        lon = c(-84.20910189917947)) %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_cri, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_cri.csv"))

@@

There is not much information on locations of aquaculture facilities. However, this shows "Mandapam Hatchery" 80000 tonnes of marine finfish in 2015... The total for 2017 is 96000. I think it is reasonable to place a point on Mandapam, at the CMFRI farm, and leave it at that. 
http://www.cmfri.org.in/division/mariculture

9.28696221512509, 79.13007737814245

>>>>

#  [1] "Albania"                  "Australia"                "Bangladesh"               "Cambodia"                
#  [5] "China"                    "China, Hong Kong SAR"     "Costa Rica"               "Croatia"                 
#  [9] "Cyprus"                   "Egypt"                    "France"                   "Greece"                  
# [13] "India"                    "Indonesia"                "Iran (Islamic Rep. of)"   "Israel"                  
# [17] "Italy"                    "Japan"                    "Korea, Republic of"       "Malaysia"                
# [21] "Malta"                    "Mauritius"                "Mexico"                   "Norway"                  
# [25] "Panama"                   "Philippines"              "Portugal"                 "Saudi Arabia"            
# [29] "Singapore"                "Spain"                    "Taiwan Province of China" "Thailand"                
# [33] "Tunisia"                  "Turkey"                   "United Arab Emirates"     "United States of America"
# [37] "Viet Nam"

@@

Now we will map the remaining countries with shrimp farms. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are not exact locations or comprehensive locations, find the number of farms. 
 - If there is no information at all, note it. We will gapfill later.

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1).

5: Comprehensive number of exact farms

4: Subset of exact locations, need to add a specific number of farms to existing locations. 
  - country|species|farm locations
  - country|species|additional points

3: A specific number of farms are known, but no locations 
 - country|species|additional points

2.5: A specific number of farms that are not comprehensive, so we will have to gapfill on top of those, if necessary. 
 - country, species, n_existing_points

2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.

1: No information on number of farms at all. Need to be gapfilled by tonnage. 
 - country|species|# additional farms (this will be NA)

## Read in ASC data
https://gis.asc-aqua.org/arcgis_app/
Maps from ASC

@@

# read in shp
farms_all <- ASC_finfish %>%
  cbind(iso) %>%
  dplyr::filter(!(crt_cnt %in% c("Denmark", "Germany", "Netherlands", "Greece", "Spain"))) ## don't need Spain or greece since it is already represented in EMODnet data

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c)

## save farm location
write.csv(farms_all_fin, here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv"), row.names = FALSE)

Now we need to map for each country, and assign a flag for gapfilling which will be completed later. I will start with all of the countries list in the ASC data.

## Turkey

Need to add 301 points to existing 22 (a final total of 323 points)

Data is from the ASC so it is a subset.

However, the FAO gives us specific numbers: http://www.fao.org/fishery/countrysector/naso_turkey/en
 - 309 Seabass/seabream farms 
 - 1 seabass farm, 13 seabass and bream and new species

 Data quality = 4

```{r}
farms_tur <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "TUR") %>%
  mutate(data_quality = 4)

write_csv(farms_tur, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_tur.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
tur_additional <- data.frame(iso3c = "TUR", type = "marine_fish_general", num_additional_farms = 301, data_quality = 4, total_farms = 323)
write.csv(tur_additional, here("marine/marine_fish_general/finfish_farms/data/subset_known_add_points_4/add_farms_tur.csv"), row.names = FALSE)
```

## Croatia

Need to add 48 points to existing 11 (a final total of 59 points)

Current data is 11 points from ASC

This claims there are 59 total farms in Croatia, so we will add more to the current points there: 
Lukin, A., 2014. Spatial Planning For Marine Aquaculture, Croatia, Zadar County Case. Croatian Ministry of Agriculture, Directorate of Fisheries.

```{r}
farms_hrv <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "HRV") %>%
  mutate(data_quality = 4)

write_csv(farms_hrv, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_hrv.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
hrv_additional <- data.frame(iso3c = "HRV", type = "marine_fish_general", num_additional_farms = 48, data_quality = 4, total_farms = 59)
write.csv(hrv_additional, here("marine/marine_fish_general/finfish_farms/data/subset_known_add_points_4/add_farms_hrv.csv"), row.names = FALSE)
```

## Albania

Need to add 22 points to existing 1 (a final total of 23 points)

Current data is from the ASC, which is a subset of farms.

http://www.fao.org/fishery/countrysector/naso_albania/en
“There are 23 marine cage farms, all of them situated in the Ionic Sea. They produce sea bream and sea bass”

```{r}
farms_alb <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "ALB") %>%
  mutate(data_quality = 4)

write_csv(farms_alb, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_alb.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
alb_additional <- data.frame(iso3c = "ALB", type = "marine_fish_general", num_additional_farms = 22, data_quality = 4, total_farms = 23)
write.csv(alb_additional, here("marine/marine_fish_general/finfish_farms/data/subset_known_add_points_4/add_farms_alb.csv"), row.names = FALSE)
```

## Japan
Current data is from ASC, only 8 farms, so definitely not comprehensive, just a drop in the bucket compared to the production of Japan. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_jpn <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "JPN") %>%
  mutate(data_quality = 2)

write_csv(farms_jpn, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_jpn.csv"))

## Australia 
Current data is from ASC, only 5 farms, so probably not comprehensive. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_aus <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "AUS") %>%
  mutate(data_quality = 2)

write_csv(farms_aus, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_aus.csv"))

## Mexico

Current data is from ASC, only 2 farms, so maybe not comprehensive. There are likely more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_mex <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "MEX") %>%
  mutate(data_quality = 2)

write_csv(farms_mex, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_mex.csv"))

## Panama
Current data is from ASC, only 1 farms, so probably not comprehensive. There are likely more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_pan <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "PAN") %>%
  mutate(data_quality = 2)

write_csv(farms_pan, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_pan.csv"))

## USA
Current data is from ASC, only 1 farms, so definitely not comprehensive. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_usa <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "USA") %>%
  mutate(data_quality = 2)

write_csv(farms_usa, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_usa.csv"))

## Viet Nam
Current data is from ASC, only 5 farms, so definitely not comprehensive, just a drop in the bucket compared to the production of Viet Nam. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_vnm <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "VNM") %>%
  mutate(data_quality = 2)

write_csv(farms_vnm, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_vnm.csv"))

## Thailand
Current data is from ASC, only 1 farms, so definitely not comprehensive, just a drop in the bucket compared to the production of Thailand. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_tha <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "THA") %>%
  mutate(data_quality = 2)

write_csv(farms_tha, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_tha.csv"))

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Cyprus" ~ "CYP", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Greece" ~ "GRC",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 5)

write_csv(farms_eu_final, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_ESP_CYP_NOR_GRC_MLT.csv"))

@@

## Italy
From http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/italy/en/
 - We will use these as existing farm points, but need to add the remaining farms that are known about.

Source:
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/

Need to add 81 points to existing 9 (a final total of 90 points)

Only a subset of points based on NASO satellite maps

However FAO reports there were 90 finfish farms in 2013...

"Ninety farms (11 percent of the total number of aquaculture farms) operated in 2013. Seabass and seabream as well as other species such as grey mullets and European eel are also cultured under extensive and semi-extensive conditions in coastal areas (e.g. “valli”, ponds and lagoons) of the northern Adriatic regions and in Sardinia, Sicily, Apulia and Lazio."
http://www.fao.org/fishery/countrysector/naso_italy/en

@@

farms_ita <- data.frame(do.call(rbind, st_geometry(ita_pts_latlon))) 
names(farms_ita) <- c("lon", "lat")
farms_ita <- farms_ita %>%
  mutate(iso3c="ITA") %>%
  mutate(data_quality = 4)

write_csv(farms_ita, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_ita.csv"))

@@

mapview(farms_ita)

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
ita_additional <- data.frame(iso3c = "ITA", type = "marine_fish_general", num_additional_farms = 81, data_quality = 4, total_farms = 90)
write.csv(ita_additional, here("marine/marine_fish_general/finfish_farms/data/subset_known_add_points_4/add_farms_ita.csv"), row.names = FALSE)
```

@@

Source:
NASO aquaculture maps collection , 2010. Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites

 - These are both not comprehensive, and I can't find any information on specific numbers of farms. So both will be labeled as data quality = 2 and need to be gapfilled based on the remaining tonnes.

@@

farms_fra <- data.frame(do.call(rbind, st_geometry(fra_pts_latlon))) 
names(farms_fra) <- c("lon", "lat")
farms_fra <- farms_fra %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "France", "FRA", "ISR")) %>%
  dplyr::select(-country, -geometry) %>%
  mutate(data_quality = 2)

write_csv(farms_fra, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_fra_isr.csv"))

@@

Source: 
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/

Current data is a subset, only 6 farms, so definitely not comprehensive, just a drop in the bucket compared to the production of Indonesia. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

@@

@@

farms_idn <- data.frame(do.call(rbind, st_geometry(idn_pts_latlon))) 
names(farms_idn) <- c("lon", "lat")
farms_idn <- farms_idn %>%
  mutate(iso3c = "IDN") %>%
  mutate(data_quality = 2)

write_csv(farms_idn, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_idn.csv"))

## Portugal
 - https://www.ine.pt/xportal/xmain?xpid=INE&xpgid=ine_publicacoes&PUBLICACOESpub_boui=435690295&PUBLICACOESmodo=2&fbclid=IwAR0-_SHYtw2XGUAXdx71RGer284Vk_u40HYKXyJzeFbpdnsHydKgAfomTvU
 - National Institute of Statistics for Portugal 
 - There is a csv table, "q5_1.csv", which has the number of farms listed by type of system. I will assume that tanks are for finfish, since [this website](https://rea.apambiente.pt/content/aquaculture-production?language=en) says that the tanks are for **fish production**, and floating structures are for **bivalve molluscs**. Located here "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Portugal/EPesca_2019.xlsx"
 - According to the table, by these criteria, there are 112 marine tank farm systems in Portugal. 
 - I will equally allocate 112 points along the coast of Portugal in suitable locations.

Source: 
Estatísticas da Pesca, 2020. Instituto Nacional de Estatística. [Accessed December 21, 2020]

```{r}
farms_prt <- data.frame(iso3c = "PRT", type = "marine_fish_general", num_additional_farms = 112, data_quality = 3)

write_csv(farms_prt, here("marine/marine_fish_general/finfish_farms/data/known_number_farms_3/farms_prt.csv"))

@@

The only species the FAO reports for Iran is "Marine fishes nei", and I can't find any information on number of marine farms there might be in Iran. This will have to be fully gapfilled.

@@

```{r}
irn_gf <- data.frame(iso3c = "IRN", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
write_csv(irn_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_irn.csv"))

## China 
Can't find any datasets of marine finfish farm locations in China. This will need to be fully gapfilled.

@@

```{r}
chn_gf <- data.frame(iso3c = "CHN", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
write_csv(chn_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_chn.csv"))

@@

 - I beleive this is comprehensive.

@@

farms_sau <- data.frame(lat = c(20.27293672234808),
                        lon = c(40.03614937279944)) %>%
  mutate(iso3c = "SAU") %>%
  mutate(data_quality = 5)

write_csv(farms_sau, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_sau.csv"))

@@

Can't find any datasets of marine finfish farm locations. This will need to be fully gapfilled.

@@

```{r}
mus_gf <- data.frame(iso3c = "MUS", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
write_csv(mus_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_mus.csv"))

@@

farms_are <- data.frame(lat = c(25.604715925918068),
                        lon = c(56.340214330776234)) %>%
  mutate(iso3c = "ARE") %>%
  mutate(data_quality = 5)

write_csv(farms_are, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_are.csv"))

@@

 - I'll place 20 points along the coast of Monastir in suitable locations.

@@

```{r}
farms_tun <- data.frame(iso3c = "TUN", type = "marine_fish_general", num_additional_farms = 20, data_quality = 3)

write_csv(farms_tun, here("marine/marine_fish_general/finfish_farms/data/known_number_farms_3/farms_tun.csv"))
```

@@

Milkfish:
https://digitalarchive.worldfishcenter.org/bitstream/handle/20.500.12348/3610/Pub%20TR4%206.pdf?sequence=1&isAllowed=y
 - I will use the respondents from the survey, and place the appropriate number of points in each location (table located on page 6, I will only use "gatherers"). This is a really old paper, but it is the best I can find. 42 total points.

@@

Combine milkfish and grouper points. These are not comprehensive points, so the rest of the production is going to need to be gapfilled.

```{r}
all_points_twn <- rbind(milkfish_points, grouper_points) %>%
  dplyr::mutate(iso3c = "TWN") %>%
  mutate(data_quality = 2)

@@

## write to farms folder 
write_csv(all_points_twn, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_twn.csv"))

@@

9.423478373794573, -

 - This is likely just a subset of total farms, so I will gapfill the remaining production. Data quality = 2

@@

```{r}
farms_cri <- data.frame(lat = c(9.423478373794573),
                        lon = c(-84.20910189917947)) %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 2)

write_csv(farms_cri, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_cri.csv"))

@@

There is not much information on locations of aquaculture facilities. This will be fully gapfilled.

http://www.cmfri.org.in/division/mariculture
